{\Large Contextual Learning via Integrated Least Effort Knowledge Networks}

### 2016-09-23 proposal.tex
added more sources

\title{{\Large Contextual learning via integrated least effort knowledge networks}}
\author{Lucas E. Morales \texttt{\{lucasem\}}}
\date{}

@@

This project introduces the knowledge network (KN) framework, capable of
contextualizing knowledge in an abstract manner. Knowledge can be
represented as distinct atoms of information and their relations in the
structure of a connected network. The network is constructed by preferential
``least effort'' attachment \cite{cancho03}, where the learning of a new
atom of knowledge joins the network with relations to the contextual
knowledge from which it was learned. This network conforms to a mathematical
pattern known as Zipf's Law \cite{zipf49}, where the degree of connectivity
for nodes in the network follow a class of power law distributions
\cite{barabasi99}. A similar pattern arises in social networks, the webgraph
of the Internet, and the statistics of linguistic distribution
\cite{clauset09}.

@@

General-purpose learning mechanisms include hierarchical Bayesian methods
\cite{tenenbaum01}, program learning \cite{lake15}\cite{liang10}, inductive
logic programming \cite{lavrac94}, and generative adversarial networks
\cite{goodfellow14}.

@@

\begin{thebibliography}{}
  \bibitem{cancho03} i Cancho, R. F., \& Ricard V. Solé. (2003)
    Least effort and the origins of scaling in human language.
    In \emph{Proceedings of the National Academy of Sciences} 100(3), 788-791.
  \bibitem{zipf49} Zipf, G. K. (1949).
    Human Behaviour and the Principle of Least-Effort.
  \bibitem{barabasi99}
    Barab\'asi, A. L., \& Albert, R. (1999).
    Emergence of scaling in random networks.
    \emph{Science}, 286(5439), 509-512.
  \bibitem{clauset09} Clauset A., Shalizi, C. R., \& Newman M. E. J.  (2009)
    Power-law distributions in empirical data.
    \emph{SIAM Review} 51(4), 661-703 (arXiv:0706.1062, doi:10.1137/070710111)
  \bibitem{serre07}
    Serre, T., Oliva, A., \& Poggio, T. (2007).
    A feedforward architecture accounts for rapid categorization.
    In \emph{Proceedings of the National Academy of Sciences}, 104(15), 6424-6429.
  \bibitem{lake15} Lake, B. M., Salakhutdinov, R., \& Tenenbaum, J. B. (2015).
    Human-level concept learning through probabilistic program induction.
    \emph{Science}, 350(6266), 1332-1338.
  \bibitem{kulkarni15}
    Kulkarni, T. D., Whitney, W. F., Kohli, P., \& Tenenbaum, J. (2015).
      Deep convolutional inverse graphics network.
      In \emph{Advances in Neural Information Processing Systems} (pp. 2539-2547).
  \bibitem{mcdermott11}
    McDermott, J. H., \& Simoncelli, E. P. (2011).
      Sound texture perception via statistics of the auditory periphery: evidence from sound synthesis.
      \emph{Neuron}, 71(5), 926-940.
  \bibitem{tenenbaum01}
    Tenenbaum, J. B., \& Griffiths, T. L. (2001).
      The rational basis of representativeness.
      In \emph{Proceedings of the 23rd annual conference of the Cognitive
      Science Society} (p. 103641).
  \bibitem{liang10}
    Liang, P., Jordan, M. I., \& Klein, D. (2010).
    Learning programs: a hierarchical Bayesian approach.
    \emph{International Conference on Machine Learning}: 639–646
  \bibitem{lavrac94}
    Lavrac, N., \& Dzeroski, S. (1994).
      Inductive Logic Programming.
      In \emph{WLP} (pp. 146-160).
  \bibitem{goodfellow14}
    Goodfellow, I., Pouget-Abadie, J., Mirza, M., Xu, B., Warde-Farley, D.,
      Ozair, S., ... \& Bengio, Y. (2014).
      Generative adversarial nets.
      In \emph{Advances in Neural Information Processing Systems} (pp. 2672-2680).
\end{thebibliography}

>>>>

\title{{\Large Contextual Learning via Integrated Least Effort Knowledge Networks}}
\author{Lucas E. Morales \texttt{\{lucasem\}}}
\date{}

@@

This project introduces the knowledge network framework, capable of
contextualizing knowledge in an abstract manner. Knowledge can be
represented as distinct atoms of information and their relations in the
structure of a connected network. The network is constructed by preferential
``least effort'' attachment \cite{cancho03}, where the learning of a new
atom of knowledge joins the network with relations to the contextual
knowledge from which it was learned. This network conforms to a mathematical
pattern known as Zipf's Law \cite{zipf49}, where the degree of connectivity
for nodes in the network follow a class of power law distributions
\cite{barabasi99}. A similar pattern arises in social networks, the webgraph
of the Internet, and the statistics of linguistic distribution
\cite{clauset09}.

@@

General-purpose learning mechanisms include hierarchical Bayesian methods
\cite{tenenbaum01}, program learning \cite{liang10}\cite{dechter13},
inductive logic programming \cite{lavrac94}\cite{muggleton15}, and
generative adversarial networks \cite{goodfellow14}.

@@

\begin{thebibliography}{}
  \bibitem{cancho03} i Cancho, R. F., \& Ricard V. Solé. (2003)
    Least effort and the origins of scaling in human language.
    In \emph{Proceedings of the National Academy of Sciences} 100(3), 788-791.
  \bibitem{zipf49} Zipf, G. K. (1949).
    Human Behaviour and the Principle of Least-Effort.
  \bibitem{barabasi99}
    Barab\'asi, A. L., \& Albert, R. (1999).
    Emergence of scaling in random networks.
    \emph{Science}, 286(5439), 509-512.
  \bibitem{clauset09} Clauset A., Shalizi, C. R., \& Newman M. E. J.  (2009)
    Power-law distributions in empirical data.
    \emph{SIAM Review} 51(4), 661-703 (arXiv:0706.1062, doi:10.1137/070710111)
  \bibitem{serre07}
    Serre, T., Oliva, A., \& Poggio, T. (2007).
    A feedforward architecture accounts for rapid categorization.
    In \emph{Proceedings of the National Academy of Sciences}, 104(15), 6424-6429.
  \bibitem{lake15} Lake, B. M., Salakhutdinov, R., \& Tenenbaum, J. B. (2015).
    Human-level concept learning through probabilistic program induction.
    \emph{Science}, 350(6266), 1332-1338.
  \bibitem{kulkarni15}
    Kulkarni, T. D., Whitney, W. F., Kohli, P., \& Tenenbaum, J. (2015).
    Deep convolutional inverse graphics network.
    In \emph{Advances in Neural Information Processing Systems} (pp. 2539-2547).
  \bibitem{mcdermott11}
    McDermott, J. H., \& Simoncelli, E. P. (2011).
    Sound texture perception via statistics of the auditory periphery:
    evidence from sound synthesis.
    \emph{Neuron}, 71(5), 926-940.
  \bibitem{tenenbaum01}
    Tenenbaum, J. B., \& Griffiths, T. L. (2001).
    The rational basis of representativeness.
    In \emph{Proceedings of the 23rd annual conference of the Cognitive
    Science Society} (p. 103641).
  \bibitem{liang10}
    Liang, P., Jordan, M. I., \& Klein, D. (2010).
    Learning programs: a hierarchical Bayesian approach.
    \emph{International Conference on Machine Learning}: 639–646
  \bibitem{dechter13}
    Dechter, E., Malmaud, J., Adams, R. P., \& Tenenbaum, J. B. (2013).
    Bootstrap Learning via Modular Concept Discovery.
    In \emph{IJCAI}.
  \bibitem{lavrac94}
    Lavrac, N., \& Dzeroski, S. (1994).
    Inductive Logic Programming.
    In \emph{WLP} (pp. 146-160).
  \bibitem{muggleton15}
    Muggleton, S. H., Lin, D., \& Tamaddoni-Nezhad, A. (2015).
    Meta-interpretive learning of higher-order dyadic datalog: Predicate
    invention revisited.
    \emph{Machine Learning}, 100(1), 49-73.
  \bibitem{goodfellow14}
    Goodfellow, I., Pouget-Abadie, J., Mirza, M., Xu, B., Warde-Farley, D.,
    Ozair, S., ... \& Bengio, Y. (2014).
    Generative adversarial nets.
    In \emph{Advances in Neural Information Processing Systems} (pp.
    2672-2680).
\end{thebibliography}
